\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}

### 2023-04-24 Latex/paper-resum.tex
# last changes

The following figure shows the accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}). The parameters used to run the Monte Carlo have been $k=0.003$, $\sigma=0.01$, and flat curve $r=0.01$. 
\begin{figure}[H]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
		\caption{OIS Future: MonteCarlo Simulation vs Malliavin}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=0.2]{Figures/convexity_avg_ois.jpg}
		\caption{Average OIS Future: MonteCarlo Simulation vs Malliavin}
\end{subfigure}
\caption{Convexity adjustment for compounding and average OIS}
\end{figure} 
\end{example}

>>>>

The following figures show the accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}). The parameters used to run the Monte Carlo have been $k=0.003$, $\sigma=0.01$, and flat curve $r=0.01$.

\begin{figure}[H]
	\begin{center}
		\includegraphics[scale=0.3]{Figures/convexity_ois.jpg}
	\end{center}
	\caption{OIS Future: MonteCarlo Simulation vs Malliavin}
	\label{fig:Futures}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[scale=0.3]{Figures/convexity_avg_ois.jpg}
	\end{center}
	\caption{Average OIS Future: MonteCarlo Simulation vs Malliavin}
	\label{fig:Futures}
\end{figure} 
\end{example}
